---
title: "R custom functions"
subtitle: "Definition and description of R custom functions for various scripts"
author: Kevin C Yang
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, message = F)
```

# Essential libraries

A list of essential libraries will also be necessary, so these have been compiled, with continuous updates, to be sourced using a single script.

Note that currently, the checkpoint package is used to install and load packages from the Microsoft R Application Network (MRAN), which stores daily snapshots from CRAN. This approach ensures that the packages loaded and installed have consistent versions therefore guarantees reproducibility. However, MRAN and checkpoint will be retired as of July 2023, so an alternative route will be needed.

```{r}
source("EssentialLibraries.R")
```

The list of essential libraries are:  

* Core libraries
  + tidyverse v`r packageVersion("tidyverse")`

* Data access
  + olapR v`r packageVersion("olapR")`
  + RODBC v`r packageVersion("RODBC")`
  + readxl v`r packageVersion("readxl")`

* Data wrangling
  + reshape2 v`r packageVersion("reshape2")`
  + lubridate v`r packageVersion("lubridate")`
  + magrittr v`r packageVersion("magrittr")`

* Data visualization
  + ggpubr v`r packageVersion("ggpubr")`
  + RColorBrewer v`r packageVersion("RColorBrewer")`
  + viridis v`r packageVersion("viridis")`
  + flextable v`r packageVersion("flextable")`

* Data output
  + openxlsx v`r packageVersion("openxlsx")`

# Session Info
```{r}
sessionInfo()
```

